---
title: "warm-up for DEPRESSION project"
author: "Louise"
date: "2019/7/17"
output: html_document
---

## Motivation:
  Nowadays, depression has been one of the most common mental health disorder in the world. Since some of my friends have suffered from it, I think it is necessary to get to know more about this issue.　　
  
## Purpose:  
  To find out whether there is any related variable between the number of cases and the city developement, I´ll graph two data and make them be visually compared, which are "the number of antidepressant users" and "per capita disposable income" of each city, 2017 in Taiwan. 　
  
## Resource:　　
```{r}
#中華民國統計資訊網　　
url <- "https://www.stat.gov.tw/mp.asp?mp=4"
#衛生福利部　　
url <- "https://dep.mohw.gov.tw/DeptList.html#"
#各縣市平均每人可支配所得　　
url <- "https://statdb.dgbas.gov.tw/pxweb/Dialog/includes/Excelss.gif"
#2017各縣市抗憂鬱藥物使用人數　　
url <- "https://www.mohw.gov.tw/dl-16605-eee5f1f6-b653-46ce-9931-9d8fa54959d7.html"
```

## Analysis:
```{r}
library(dplyr)
library(readxl)
hhsfile <- read_excel("C:/Users/louin/Documents/GitHub/homework2/household_statistics.xlsx")
head(hhsfile)
uotadfile <- read_excel("C:/Users/louin/Documents/GitHub/homework2/users_of_the_antidepressant_in_each_city_2017.xlsx")
head(uotadfile)

"per capita disposable income" <- select(hhsfile, city, `per capita disposable income`)
head(`per capita disposable income`)
"users of antidepressant" <- arrange(uotadfile, desc(`users of the antidepressant`))
head(`users of antidepressant`)
depression_v.s._income <- left_join(`users of antidepressant`, `per capita disposable income`, by = "city")
head(depression_v.s._income)
```

## Resault:
```{r}
library(ggplot2)
scatterplot <- (ggplot(data = depression_v.s._income, aes(x=`users of the antidepressant`, y=`per capita disposable income`, color="sex")) + 
   ggtitle("2017 Depression v.s. Disposable Income"))
scatterplot + geom_point(alpha = .7, size = 3)  
```

```{r}  
scatterplot + geom_line()  
```

```{r}  
scatterplot + geom_point(alpha = .7, size = 3) + geom_smooth(method = "lm")
```　　

## Conclusion:  
  All of the graphs above show that the users of the antidepressant and the city developement are positively related, maybe the data is not that obvious, still, due to the linear regression, the hypothesis of whether there is any dependent variable has not be rejected.
  
## Next Action:
  I would like start from edcuational background.